### 2019-03-18 manuscript.tex
Edit in github
Push with Chyun

\newcommand{\comment}[1]{\textbf{[[#1]]}}
\newcommand{\cfcmt}[1]{\comment{CFS: #1}}
\newcommand{\cf}[1]{\comment{CFS only: #1}}
\newcommand{\jdcmt}[1]{\comment{JD: #1}}
\newcommand{\jdmlcmt}[1]{\comment{JDML: #1}}
\newcommand{\mlcmt}[1]{\comment{MLi: #1}}

@@

Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
\cfcmb{This title is a rebuttal to Efferson’s title}

@@

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low. I would
expect a majority under 15, no?}\cf{Most of the surveys sampled women of 15-49, girls under 15 were reported by their mothers. The ration of girls under 15 is minority} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (updated Sep 18).  United Nation has declared zero tolerance for FGC as it violates human rights and promoted the abundance of the practice  \cite{}.  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jd{This claim is surprising, and the sources are not
academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}. Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision;
we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

>>>>

\newcommand{\comment}[1]{\textbf{[[#1]]}}
\newcommand{\cfcmt}[1]{\comment{CFS: #1}}
\newcommand{\cf}[1]{\comment{CFS only: #1}}
\newcommand{\jdcmt}[1]{\comment{JD: #1}}
\newcommand{\mlcmt}[1]{\comment{MLi: #1}}

@@

Female Genital Cutting Is a Social Coordination Norm in Kenya, Mali, Nigeria and Sierra Leon
\cfcmt{This title is a response to Efferson’s title}

@@

It is estimated that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East \cite{UNFPA14, UNIC16} \cf{updated Sep 18}.  The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{}.  Current progress of in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jdcmt{This claim is surprising, and the sources are not
academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}. \jdcmt{Not all UN sources are the same. The factsheet does not even seem to say that.} Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision;
we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).
